


\documentclass[a4paper]{deedy-resume} 
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage[most]{tcolorbox}


\begin{document}

\namesection{Vishakh}{Kumar} 

\href{vkumar@gatech.edu}{vkumar@gatech.edu} | 404.985.6530  

\begin{minipage}[t]{0.35\textwidth} 

\section{Education} 
\subsection{Georgia Tech}
\descript{BS in Aerospace Engineering}
\location{Expected Graduation | Aug 2019}
Minor in Computational Data Analysis
\sectionspace 
\section{CAD Projects} 
  \descript{\underline{Hydroponic Vase}}  Provides running water to a six segmented vase. Provides a staggered flow of water to the vase. 3-D printable using ABS plastic. {\bf Submitted} at {\bf GrabCAD 3D Hydroponics System Challenge}\\ 
  \descript{\underline{Portable French Press}} Features an inbuilt grinder, french press and thermos. Features customization for temperature, procedure time and grind grade. Used to make coffee with limited equipment and space. {\bf Submitted} at {\bf Sustainability Design-a-Thon 2016}
\section{Github Projects} 
  \href{https://github.com/vishakhkumar/arduinoLibrary}{\descript{\underline{arduinoSetup}}}  Website that takes the Arduino IDE and installs any library specified. Provides a one-step install tool for users new to the Arduino. Won {\bf Best Developer Prize} at {\bf PearlHacks 2016}\\
  \href{https://github.com/vishakhkumar/RIP}{\descript{\underline{RIP}}}  Website that takes video from Youtube, strips required audio and stores it for use by Garageband. Used to simplify the process of sampling music and making a sick beat. Won {\bf Overall Prize} at {\bf Hack the Beat 2016.}\\ 
  
  \href{https://github.com/vishakhkumar/HyperPlane}{\descript{\underline{HyperPlane}}} visualizes the rotation of 4-D objects in 3-D space using Processing. {\bf Demoed at HackFSU 2016}\\ 
  
  \href{https://github.com/vishakhkumar/autoScript}{\descript{\underline{autoScript}}}  Installs developer and productivity tools on a computer so that I can work on any system. Used to improve productivity while working on unknown computers. \\
  
 \href{https://github.com/vishakhkumar/AE1600glider}{\descript{\underline{AE1600glider}}}  Generates a glider in OpenScad using Python. Generates information such as drag and lift.
Optimizes a balsa glider for maximum distance. \\

\sectionspace 

\end{minipage} 
\hspace*{.04\textwidth}
\begin{minipage}[t]{0.58\textwidth} 

\section{Experience}

\runsubsection{HyTech Racing}
\descript{| Composites + CFD Engineer}
\location{August 2016 – Current | Atlanta, GA}
\vspace{\topsep} 
\begin{tightitemize}
\item Involved in designing front airfoils for SAE car.
\item Gained certification in water jet cutting with the MAXIEM 1515 
\item Gained certification in CNC routing with CamWood Model:WR408 \\
\item Website:// \href{https://hytechracing.gatech.edu/}{\bf HyTechRacing.gatech.edu}
\end{tightitemize}
\sectionspace 

\runsubsection{Adroit Infinitum}
\descript{| Design + Manufacturing Engineer}
\location{June 2012 – May 2013 | Dubai, UAE}
\vspace{\topsep} 
\begin{tightitemize}
\item Awarded the Social Media Prize held at Austin, Texas
\item Awarded the National Champions at Yas Marina, Abu Dhabi.
\item Designed and Manufactured the car for the F1 in Schools Competition primarily in Solidworks with elements in OpenSCAD.
\item Tested aerodynamic features in Simulink. 
\item Gained experience with CNC machining and plastic material, especially HDPE. \\
\item Facebook:// \href{https://www.facebook.com/AdroitInfinitum}{\bf AdroitInfinitum}
\end{tightitemize}
\sectionspace 

\runsubsection{Split Second}
\descript{| Design + Manufacturing Engineer}
\location{June 2011 – June 2012 | Dubai, UAE}
\begin{tightitemize}
\item Awarded the First Prize for Team Identity held at Yas Marina, Abu Dhabi 
\item Worked on designing and manufacturing the car for the F1 in Schools Competition primarily in Solidworks. 
\item Assisted junior teams inexperienced in Solidworks.
\end{tightitemize}
\sectionspace 


\section{Research}
\runsubsection{ASDL - Georgia Tech}
\descript{| Assistant Undergraduate Researcher}
\location{Mar 2014 – May 2015 | Atlanta, GA}
\begin{tightitemize}
\item Analysis of motor Performance in Electric Motors for N+3 Aircraft and Hybrid Design.
\item Created database of electric motors with specifications.
\end{tightitemize}
\sectionspace 



\section{Skills}
\noindent
\begin{minipage}[t]{.45\textwidth}
{
\subsection{Programming}
 Haskell 
 \textbullet{} Python
 \textbullet{} C  
 \textbullet{} Flask
 \textbullet{} MATLab  
 \textbullet{} Microsoft Excel with VBA \& Xlwings 
 \textbullet{} \LaTeX\ 
 }
\end{minipage}% <---------------- Note the use of "%"
\hspace*{.05\textwidth}
\begin{minipage}[t]{.49\textwidth}
{ \subsection{CAD}
 Solidworks  
 \textbullet{} Autodesk Fusion 360 \textbullet{} Google Sketchup \textbullet{} Antimony \textbullet{} OpenSCAD}
\end{minipage}

\sectionspace 
\begin{comment}
\section{High School Activities and Awards} 
\begin{tabular}{rll}
2015	 & National  		& 4066 - Rank for JEE (Advanced) 2015 \\
2015     & School    		&Valedictorian in Blessing Ceremony \\
2015     & Inter-School 	& Master of Ceremony in Sahodaya Award Ceremony \\
2015     & National 		& Finalist in IESO 2015 - Indian Earth Science Olympiad \\
2015     & School           & Highest score in school - awarded cash prize \\
2014     & National 		& 70\% in Senior National Mathematics Olympiad Contest \\
2013	 & International 	& Round Square South Asia / Gulf Region Conference \\
2012     & School 			& Student Council Member, Indian High School, Dubai \\
2012     & School           & President, Gavel Club, Indian High School, Dubai \\
2012     & International    & Certificate of Distinction –Maths \& Science - ASSET \\
\end{tabular}
\end{comment}

\sectionspace 

\end{minipage}

\end{document}

